---
title: "Africa CDC Colours, Palettes, and Themes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Africa CDC Colours, Palettes, and Themes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "ragg_png"
)
```

```{r setup, echo = FALSE}
library(paleta)
library(ggplot2)
```

[Africa Centres for Disease Control and Prevention (Africa CDC)](https://africacdc.org) is a specialised technical institution of the African Union established to support public health initiatives of Member States and strengthen the capacity of their public health institutions to detect, prevent, control and respond quickly and effectively to disease threats.


## Africa CDC vision and mission

* A safer, healthier, integrated and prosperous Africa, in which Member States can efficiently prevent disease transmission, implement surveillance and detection, and always be prepared to respond effectively to health threats and outbreaks.

* To strengthen the capacity, capability and partnerships of Africa’s public health institutions to detect and respond quickly and effectively to disease threats and outbreaks based on science, policy and data-driven interventions and programmes.


## Africa CDC values

* Professionalism

* Equity

* Evidence-based decision-making

* Integrity

* Excellence


## Africa CDC Colours

The Africa CDC employs three primary colours: Green, Gold and Red.

```{r acdc-primary, echo = FALSE, fig.alt = "Africa CDC primary palette of 3 colours", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_primary, class = "palette", name = "Africa CDC Primary Colours")
```

These are complemented by a set of eleven secondary colours.

```{r acdc-secondary, echo = FALSE, fig.alt = "Africa CDC secondary palette of 11 colours", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_secondary, class = "palette", name = "Africa CDC Secondary Colours")
```

## Africa CDC Palettes

In addition to the primary and secondary colours, a set of tinted palettes for each Africa CDC secondary colour is available.

### Tinted blue palette

```{r acdc-blue-tint, echo = FALSE, fig.alt = "Africa CDC tinted blue palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_blues, class = "palette", name = "Africa CDC Blues")
```

### Tinted plum palette

```{r acdc-plum-tint, echo = FALSE, fig.alt = "Africa CDC tinted plum palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_plums, class = "palette", name = "Africa CDC Plums")
```

### Tinted blue grey palette

```{r acdc-bluegrey-tint, echo = FALSE, fig.alt = "Africa CDC tinted blue grey palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_blue_greys, class = "palette", name = "Africa CDC Blue Greys")
```

### Tinted amber palette

```{r acdc-amber-tint, echo = FALSE, fig.alt = "Africa CDC tinted amber palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_ambers, class = "palette", name = "Africa CDC Ambers")
```

### Tinted cyan palette

```{r acdc-cyan-tint, echo = FALSE, fig.alt = "Africa CDC tinted cyan palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_cyans, class = "palette", name = "Africa CDC Cyans")
```

### Tinted deep orange palette

```{r acdc-deeporange-tint, echo = FALSE, fig.alt = "Africa CDC tinted deep orange palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_deep_oranges, class = "palette", name = "Africa CDC Deep Oranges")
```

### Tinted purple palette

```{r acdc-purple-tint, echo = FALSE, fig.alt = "Africa CDC tinted purple palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_purples, class = "palette", name = "Africa CDC Purples")
```

### Tinted lime palette

```{r acdc-lime-tint, echo = FALSE, fig.alt = "Africa CDC tinted lime palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_limes, class = "palette", name = "Africa CDC Limes")
```

### Tinted mauve palette

```{r acdc-mauve-tint, echo = FALSE, fig.alt = "Africa CDC tinted mauve palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_mauves, class = "palette", name = "Africa CDC Mauves")
```

### Tinted pink palette

```{r acdc-pink-tint, echo = FALSE, fig.alt = "Africa CDC tinted pink palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_pinks, class = "palette", name = "Africa CDC Pinks")
```

### Tinted teal palette

```{r acdc-teal-tint, echo = FALSE, fig.alt = "Africa CDC tinted teal palette", fig.align = "center", fig.height = 1}
structure(acdc_palettes$acdc_teals, class = "palette", name = "Africa CDC Teals")
```

## Africa CDC `ggplot2` theme

### Africa CDC light theme

```{r mtcars-acdc-light-bar, echo = FALSE, fig.align = "center", fig.alt = "A bar plot showcasing the Africa CDC light theme", fig.showtext = TRUE, fig.height = 6, fig.width = 5, fig.retina = 1}
## barplot using theme_acdc_light
ggplot(
  data = mtcars,
  mapping = aes(
  x = factor(vs, levels = c(0, 1), labels = c("v-shaped", "straight")),
  fill = factor(cyl))
) +
  geom_bar() +
  scale_fill_manual(name = "Cylinders", values = acdc_palettes$acdc_secondary) +
  labs(
    title = "Light ACDC Theme",
    subtitle = "Using the Africa CDC secondary palette",
    x = "Engine Shape", y = "Counts"
  ) +
  theme_acdc_light(grid = "Y")
```

```{r mtcars-acdc-light-scatter, echo = FALSE, fig.align = "center", fig.alt = "A scatter plot showcasing the Africa CDC light theme", fig.showtext = TRUE, fig.height = 6, fig.width = 5, fig.retina = 1}
## scatterplot using theme_acdc_light
ggplot(data = mtcars, mapping = aes(x = mpg, y = disp, colour = factor(cyl))) +
  geom_point(size = 3) +
  scale_colour_manual(
    name = "Cylinders", 
    values = acdc_palettes$acdc_secondary
  ) +
  labs(
    title = "Light ACDC Theme",
    subtitle = "Using the Africa CDC secondary palette",
  ) +
  theme_acdc_light(grid = "XY")
```


### Africa CDC dark theme

```{r mtcars-acdc-dark-bar, echo = FALSE, fig.align = "center", fig.alt = "A bar plot showcasing the Africa CDC dark theme", fig.showtext = TRUE, fig.height = 6, fig.width = 5, fig.retina = 1}
## barplot using theme_acdc_dark
ggplot(
  data = mtcars,
  mapping = aes(
  x = factor(vs, levels = c(0, 1), labels = c("v-shaped", "straight")),
  fill = factor(cyl))
) +
  geom_bar() +
  scale_fill_manual(name = "Cylinders", values = acdc_palettes$acdc_secondary) +
  labs(
    title = "Dark ACDC Theme",
    subtitle = "Using the Africa CDC secondary palette",
    x = "Engine Shape", y = "Counts"
  ) +
  theme_acdc_dark(grid = "Y")
```

```{r mtcars-acdc-dark-scatter, echo = FALSE, fig.align = "center", fig.alt = "A scatter plot showcasing the Africa CDC dark theme", fig.showtext = TRUE, fig.height = 6, fig.width = 5, fig.retina = 1}
## scatterplot using theme_acdc_dark
ggplot(data = mtcars, mapping = aes(x = mpg, y = disp, colour = factor(cyl))) +
  geom_point(size = 3) +
  scale_colour_manual(
    name = "Cylinders", 
    values = acdc_palettes$acdc_secondary
  ) +
  labs(
    title = "Dark ACDC Theme",
    subtitle = "Using the Africa CDC secondary palette"
  ) +
  theme_acdc_dark(grid = "XY")
```
