---
title: "Global Nutrition Cluster Colours, Palettes, and Themes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Global Nutrition Cluster Colours, Palettes, and Themes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "ragg_png"
)
```

```{r setup, echo = FALSE}
library(paleta)
library(ggplot2)
```

The Global Nutrition Cluster (GNC) is a coordination mechanism that supports nutrition responses in humanitarian emergencies. It is one of the clusters established by the Inter-Agency Standing Committee (IASC) to ensure effective and efficient humanitarian responses across various sectors, including nutrition.

## GNC colours

GNC main colour is the **GNC Green**.

```{r gnc-green, echo = FALSE, fig.alt = "GNC Green", fig.align = "center", fig.height = 1}
structure(gnc_green, class = "palette", name = "GNC Green")
```

Complementing **GNC Green** is a set of 10 secondary colours.

```{r gnc-secondary, echo = FALSE, fig.alt = "GNC secondary colours palette", fig.align = "center", fig.height = 1}
structure(gnc_palettes$gnc_secondary, class = "palette", name = "GNC Secondary")
```

## GNC `ggplot2` theme

A GNC `ggplot2` theme function called `theme_gnc()` is included in the `paleta` package. Following are examples of how it can be used.

```{r gnc-theme-bar, echo = FALSE, fig.alt = "A bar plot showcasing the GNC ggplot2 theme", fig.align = "center", fig.showtext = TRUE, fig.height = 6, fig.width = 5, fig.retina = 1}
## barplot using theme_gnc()
ggplot(
  data = mtcars,
  mapping = aes(
  x = factor(vs, levels = c(0, 1), labels = c("v-shaped", "straight")),
  fill = factor(cyl))
) +
  geom_bar() +
  scale_fill_manual(
    name = "Cylinders", 
    values = gnc_palettes$gnc_secondary
  ) +
  labs(
    title = "GNC Theme",
    subtitle = "GNC secondary palette",
    x = "Engine Shape", y = "Counts"
  ) +
  theme_gnc(grid = "Y")
```

```{r gnc-theme-scatter, echo = FALSE, fig.alt = "A scatter plot showcasing the GNC ggplot2 theme", fig.align = "center", fig.showtext = TRUE, fig.height = 6, fig.width = 5, fig.retina = 1}
## scatterplot using theme_gnc()
ggplot(data = mtcars, mapping = aes(x = mpg, y = disp, colour = factor(cyl))) +
  geom_point(size = 3) +
  scale_colour_manual(
    name = "Cylinders", 
    values = gnc_palettes$gnc_secondary
  ) +
  labs(
    title = "GNC Theme",
    subtitle = "GNC secondary palette",
  ) +
  theme_gnc(grid = "XY")
```


